---
title: "Using gfsR to import FN2 archive files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using gfsR to import FN2 archive files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(gfsR)
data("tw2")

```

The primary function of `gfsR` is to be able to import FishNet2 (FN2) `DATA.ZIP` files directly in to **R**. This is a short vignette to demonstrate some of the functionality available by using the common functions.

```{r setup}
library(gfsR)
```

The most common usage is to import a single FN2 project. This is accomplished by providing the file path directly to one of the import functions. For this example we'll use `import_fn_index_net` to import a gill net project. All functions import FN2 tables as tables in a list and thus will need to be assigned to a variable. This approach was taken to allow the option for different projects to be imported to a local environment at the same time and eventually combined as required.  

```{r import, eval=FALSE}
tw2 <- import_fn_index_net("Data/TW2/IA15_TW2/DATA.ZIP")
```

The `gfsR` functions make use of messages from the `usethis` package to provide *chatty* functions that provide indications of progress and note any tables that are not available.

A quick way to examine the data is to use `lapply` and `head`.
```{r examine-import}
lapply(tw2, head)
```

Frequently users will want to access the tables directly as dataframe in the global environment rather than as a dataframe in a list. This is quickly accomplished with the `list2env` function. **CAUTION**: using the `list2env` will overwrite existing tables in the global environment.

```{r list-2-env}
ls() # shows current variables in global environment
list2env(tw2, envir = .GlobalEnv) # to move list elements to global env.
ls() # verify all tables exist in global env.
```


